Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-18 paper/icml_drau/relatedworks.tex

More recently, \cite{dueling_nets} also introduced a parameterization separating
the value and the advantage components of the $Q$-function. Contrary to
\cite{adv_upd}'s Advantage Updating, learning is still done in a standard
way on the $Q$-function obtained from adding these two components. Thus this
approach reparameterizes $Q$ but does not change scalings
and does not result in an invariant algorithm for small $\deltat$.%We additionally
%introduce a natural scaling coeficient between the two, that strongly improves
%the time discretization invariance properties.

@@

>>>>

\cite{dueling_nets} also use a parameterization separating
the value and advantage components of the $Q$-function. But contrary to
\cite{adv_upd}'s Advantage Updating, learning is still done in a standard
way on the $Q$-function obtained from adding these two components. Thus this
approach reparameterizes $Q$ but does not change scalings
and does not result in an invariant algorithm for small $\deltat$.%We additionally
%introduce a natural scaling coefficient between the two, that strongly improves
%the time discretization invariance properties.

@@

The problem studied here is a continuity effect quite distinct from
multiscale RL approaches: indeed the issue arises even if there
is only one timescale in the environment. Arguably, a small
$\deltat$ can be seen as a mismatch between the algorithm's
timescale and the physical system's timescale, but the collapse of the
$Q$ function to the $V$ function is an intrinsic mathematical phenomenon from time
continuity, and cannot obviously be addressed via existing multiscale
techniques. \TODO{cite something!}
